Paper Analysis

### 2025-04-17 Paper_WriteUp/Paper_Plots.qmd
putting in updated code for fig3

@@

  #find rating
  games = data.frame(Week = i,
                     Player1 = users[focal_player_used],
                     Player2 = opp,
                     Score = sim_result)
  initstate = tibble(Player = c(users[focal_player_used], opp),
                     Rating = c(curr_rating, opp_elo),
                     Deviation = 50,
                     Volatility = 0.04)

>>>>

```{r figure 3 - Updated}
### Adam
#' April 17, 2025
#' adding code to updated fig3
#' only comparing gamma1, gamma2, & mu_beta across all 4 cohorts

#read in models
model_17_19 = readRDS(here("results_revision", "lichess1700-1900", "all_rated_bullet_model_prev_n1.RDS"))
model_20_22 = readRDS(here("results_revision", "lichess2000-2200", "all_rated_bullet_model_prev_n1.RDS"))
model_23_25 = readRDS(here("results_revision", "lichess2300-2500", "all_rated_bullet_model_prev_n1.RDS"))
model_gm = readRDS(here("results_revision", "lichessGrandmasters", "all_rated_bullet_model_prev_n1.RDS"))

#get global effects of each
pars_17_19 <- model_17_19$draws(c("mu_beta", "gamma1", "gamma2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"gamma2") |> 
  mutate(model = "1700-1900")

pars_20_22 = model_20_22$draws(c("mu_beta", "gamma1", "gamma2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"gamma2") |> 
  mutate(model = "2000-2200")

pars_23_25 = model_23_25$draws(c("mu_beta", "gamma1", "gamma2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"gamma2") |> 
  mutate(model = "2300-2500")

pars_gm <- model_gm$draws(c("mu_beta", "gamma1", "gamma2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"gamma2") |> 
  mutate(model = "GM")

#for plotting
facet_labels <- as_labeller(c(
  mu_beta = "mu[beta]",
  gamma1 = "gamma[1]",
  gamma2 = "gamma[2]",
  sigma_1 = "sigma[1]",
  `tau[1]` = "tau[1]",
  `tau[2]` = "tau[2]",
  sigma_g1 = "sigma[g[1]]",
  sigma_g2 = "sigma[g[2]]"
), label_parsed)

gm_amateur_comp_global <- bind_rows(pars_17_19, pars_20_22, pars_23_25, pars_gm) |> 
  ggplot(aes(x = value, y = name, color = factor(model, levels = c("1700-1900", "2000-2200", "2300-2500", "GM")))) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "H")

gm_amateur_comp_global

@@

  #find rating
  games = data.frame(Week = i,
                     Player1 = users[focal_player_used],
                     Player2 = opp,
                     Score = sim_result)
  initstate = tibble(Player = c(users[focal_player_used], opp),
                     Rating = c(curr_rating, opp_rating),
                     Deviation = 50,
                     Volatility = 0.04)
